\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{titlesec}

% Colors
\definecolor{primaryblue}{RGB}{25, 54, 109}
\definecolor{secondaryblue}{RGB}{47, 85, 151}

% Links
\hypersetup{colorlinks=true,urlcolor=secondaryblue}

% Section titles
\titleformat{\section}
  {\color{primaryblue}\normalfont\Large\bfseries}
  {}{0em}{}
  [{\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{7pt}{3pt}

% Bullet indentation & compact spacing
\setlist[itemize]{
  leftmargin=2em,
  labelsep=0.4em,
  itemsep=0.15em,
  topsep=0.15em
}

% Slightly tighter line spacing
\linespread{0.96}

\setlength{\parskip}{0pt}
\pagestyle{empty}

\begin{document}

% ===== Header =====
\begin{center}
    {\Huge \bfseries \color{primaryblue}Rohit} \\[0.3em]
    \small
    \faEnvelope~\href{mailto:rohitcodes03@gmail.com}{rohitcodes03@gmail.com} ~|~ 
    \faPhone~+91 90277 42255 ~|~
    \faLinkedin~\href{https://www.linkedin.com/in/rohiitcodes/}{rohiitcodes} ~|~
    \faGithub~\href{https://github.com/rohiitgit/}{rohiitgit}
\end{center}

\vspace{0.4em}
\noindent \textit{High-agency developer experienced in building \textbf{Webapps}, \textbf{ML pipelines}, and \textbf{AI integrations}. Comfortable contributing across stacks and learning new technologies fast.}

% ===== Skills =====
\section*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, JavaScript, C/C++, Solidity \quad \textbf{Frontend:} React, TailwindCSS, HTML, CSS
  \item \textbf{Backend:} Flask, Node.js, REST APIs \quad \textbf{ML/AI:} TensorFlow, PyTorch, OpenCV
  \item \textbf{Databases/CMS:} MongoDB, Supabase, Sanity \quad \textbf{Dev Tools:} Git, Docker, Postman
  \item \textbf{Expertise:} Machine Learning, Web Development, Automation, Computer Vision
  \item \textbf{OS:} Arch Linux, Ubuntu, Windows
\end{itemize}

% ===== Experience =====
\section*{Professional Experience}

\noindent\textbf{\href{https://www.linkedin.com/company/openblood/posts/?feedView=all}{OpenBlood}} 
\hfill \textit{Engineer Intern} — \textit{Aug 2025 – Present}
\begin{itemize}
  \item Building OpenBlood landing page with \textbf{modern design UI } and \textbf{GSAP animations}
  \item Enhanced the Open Blood app through UX/UI improvements, leading to a smoother and more intuitive user flow.
\end{itemize}
\vspace{0.4em}

\noindent\textbf{\href{https://www.boundspec.com/}{Boundspec}} 
\hfill \textit{Software Developer Engineer} — \textit{Apr 2025 – Sept 2025}
\begin{itemize}
  \item Built role-based dashboards for \textbf{doctor-patient booking} app with dynamic UI/UX.
  \item Integrated \textbf{Sanity CMS} for dynamic content across Prajna and Boundspec websites.
  \item Contributed full-stack features for production apps, using \textbf{React Native + Supabase} and various other technologies.
\end{itemize}
\vspace{0.4em}

\noindent\textbf{\href{https://in.linkedin.com/company/celebrarecompany}{Celebrare}} 
\hfill \textit{Remote Python Developer Intern} — \textit{Nov 2024 – Apr 2025}
\begin{itemize}
  \item Rewrote \textbf{face recognition pipeline} from Python to C++ achieving \textbf{5–8x performance gain}.
  \item Optimized vision models, reducing \textbf{average processing time by 91.11\%}.
  \item Maintained \textbf{99\% accuracy}, added support for multiple orientations/formats.
\end{itemize}
\vspace{0.4em}

% ===== Projects =====
\section*{Projects}

\noindent\textbf{\href{https://www.rohiit.space/}{rohiit.space}} \hfill \textit{HTML, tailwindcss, vanilla js}
\begin{itemize}
  \item modern design \textbf{portfolio} and \textbf{blog} site
  \item \textbf{UI} inspired by \textbf{tailwindcss} landing page
\end{itemize}
\vspace{0.4em}

\noindent\textbf{\href{https://fynl-it.vercel.app/}{Fynl-It}} \hfill \textit{Next.js, Supabase, Gemini AI, TailwindCSS}
\begin{itemize}
  \item Fullstack tool to \textbf{automate invoice follow-up emails} with progressive AI tone.
  \item Integrated \textbf{secure payment detection} using Razorpay UPI.
\end{itemize}
\vspace{0.4em}

\noindent\textbf{\href{https://landing-theta-red-48.vercel.app/}{Open Blood Landing Page}} \hfill \textit{HTML, CSS, Vanilla JS, GSAP, Lenis}
\begin{itemize}
  \item Designed and built landing page for nationwide blood donation network.
  \item Features modern UI with smooth animations.
\end{itemize}
\vspace{0.4em}

\noindent\textbf{\href{https://web3-referral-landing.vercel.app/}{Web3 Referral Platform Landing Page}} \hfill \textit{Next.js, TailwindCSS}
\begin{itemize}
  \item Created responsive, animated landing page for blockchain referral startup.
  \item Built reusable and performant UI components.
\end{itemize}
\vspace{0.4em}

% ===== Achievements =====
\section*{Achievements}

\noindent\textbf{\href{https://www.linkedin.com/posts/rohiitcodes_smart-india-hackathon-was-a-fabulous-experience-activity-7274397856336101376-Rh_Q?utm_source=share&utm_medium=member_desktop}{Smart India Hackathon 2024 Finalist}}
\begin{itemize}
  \item Finalist in national hackathon; built \textbf{WebGIS solution for ISRO}.
  \item Used Meta’s \textbf{Segment Anything Model v2} for precise satellite image segmentation.
\end{itemize}
\vspace{0.4em}

% % ===== Certifications =====
% \section*{Certifications}
% \begin{itemize}
%   \item \textbf{Intermediate Machine Learning}, \href{https://www.kaggle.com/learn/certification/rohiitcodes/intermediate-machine-learning}{Kaggle} \hfill Sep 2023
%   \item \textbf{Machine Learning Explainability}, \href{https://www.kaggle.com/learn/certification/rohiitcodes/machine-learning-explainability}{Kaggle} \hfill Sep 2023
% \end{itemize}

% ===== Education =====
\section*{Education}
\noindent\textbf{B.Tech in Computer Science} \hfill \textit{2021–2025 — 6.0 SGPA} \\
Dr. A.P.J. Abdul Kalam Technical University, Lucknow, UP

\end{document}
